Efficient pedigree recording for fast population genetics simulation

### 2018-01-12 forwards_paper.tex

We implemented simulations and the connection to \msprime{} in \cpp{}, using \fwdpp{} library functions and
interface code using a continuum-sites model for both mutation
and recombination. Simulations were run using \fwdpy{} (version 0.13.a0), a Python package based
on \fwdpp{} (version 0.5.7).
Code for all simulations and figures is available at \url{https://github.com/petrelharp/ftprime_ms}.
These made use of the GNU Scientific Library \citep[version 1.16][]{galassi2018scientific},
pybind11 \citep[version 2.2.1][]{pybind11},
and GCC (version 4.8.5).
We ran all benchmarks on an Ubuntu Linux (version 16.04) system with two 2.6 GHz Intel E5-2650 CPU with
hyperthreading enabled.
We ran one simulation at a time and the machine was under minimal load otherwise.
We used GNU parallel \citep{Tange2011a} to kill any simulation that did not finish within 72 hours,
and the Linux \texttt{time} command to record run time and peak memory usage of each replicate.
%% Our simulation scripts separately recorded the time spent in various steps of each run.

>>>>

We implemented simulations and the connection to \msprime{} in \cpp{}, using \fwdpp{} library functions and
interface code using a continuum-sites model for both mutation
and recombination. Simulations were run using \fwdpy{} (version 0.13.a0), a Python package based
on \fwdpp{} (version 0.5.7).  The majority of results are presented based on a single-threaded implementation.  However,
we also implemented a parallelized version using Python's \texttt{queue.Queue} to run the simplification step in a separate Python
thread. Our implementation allows a maxmimum of four simplification intervals to be in the queue at once. This
parallelized version also performed fitness calculation in parallel using two threads of execution in C++.

Code for all simulations and figures is available at \url{https://github.com/petrelharp/ftprime_ms}.
These made use of the GNU Scientific Library \citep[version 1.16][]{galassi2018scientific},
pybind11 \citep[version 2.2.1][]{pybind11},
and GCC (version 4.8.5).
We ran all benchmarks on an Ubuntu Linux (version 16.04) system with two 2.6 GHz Intel E5-2650 CPU with
hyperthreading enabled.
We ran one simulation at a time and the machine was under minimal load otherwise.
We used GNU parallel \citep{Tange2011a} to kill any simulation that did not finish within 72 hours,
and the Linux \texttt{time} command to record run time and peak memory usage of each replicate.
%% Our simulation scripts separately recorded the time spent in various steps of each run.
